\paragraph{}
This document cover the Opale project, which took place in the context inside
the Master SEME on the univeristy of Strasbourg.

\paragraph{}
This project was started on the first semester, by november 2024. The goal was
to develop a small scale rocket that modelize the behavior of real ones. This
model include the usage of powder engines, as well as come control electronics
embedded into the rocket.

\paragraph{}
For all along this report, we're going to describe all the reflexions, studies,
and conception. Since we're Electronics Engineering students, we'll focus more
on the electronics and sofware aspects, but the mechanical part will also
quicly be explained. The goal with the control electronics is to ensure the
rocket will follow a defined trajectory, as well as storing into an EEPROM some
measurements for an after fly interpretation.

The rocket can be modeled as a complex system, composed with multiple blocks :

\begin{itemize}[noitemsep]
    \item   Sensors (positionning, temperature...)
    \item   Outputs (Servos engines control, engine starter...)
    \item   Controller (MCU + Memory)
    \item   Power supplies
\end{itemize}

\paragraph{}
This report will be splitted in multiple parts, that are not ordered in a
chronological order, but more in a logic way.

\paragraph{}
In the first chapter, we're going to explain how we choosed main hardware
elements, such as the controller, the servo engines or the inertial measurement
unit. These are device where a wide range of choices are possible !

In a second part, we'll focus on the caracterisation of sensors and actuators,
to understand precisely how they behave to any input signals. This is an
important step if we want to develop a precise controller for them !

For a third chapter, we're going to detail the whole procedure of the
electronic design. This start from the schematic, and end up with a whole
printed circuit board, ready to be manufactured.

For the next part, we'll see how we designed the controller of the rocket, from
the physical equations to a simulation, and then implemented into an embedded
controller.

And, to finish the main section, a final part will be dedicated for the whole
software we wrote, that handle the control as well as some other task on the
rocket.

After the conclusion, in annexes there will be some more details. This include
a mechanical overview of the rocket, as well as the process of soldering the
board or some precisions about the software and controller we developped.

