\section{RTOS}\label{annex:RTOS}
For this second part, we'll go a bit higher in the software structure of the
project, and see the different layers. The first layer is the one we'll
describe here, which is the RTOS.

This stand for Real Time Operating System.

\begin{quote}
    \quote{A real-time operating system (RTOS) is an operating system (OS) for real-time
        computing applications that processes data and events that have critically defined
        time constraints. A RTOS is distinct from a time-sharing operating system, such as
        Unix, which manages the sharing of system resources with a scheduler, data buffers,
        or fixed task prioritization in multitasking or multiprogramming environments. All
        operations must verifiably complete within given time and resource constraints or
        else fail safe. Real-time operating systems are event-driven and preemptive, meaning
        the OS can monitor the relevant priority of competing tasks, and make changes to
        the task priority.}
    \cite{RTOS}
\end{quote}

\paragraph{}
Thus, we're able to specify strict time constraints for different threads. This
is very usefull, since it enable us to ensure the controller, designed for a
specific sampling rate will iterate at a defined speed.

\subsection{Basic RTOS concepts}
To match they're requirements, near all of the RTOS define some basic concepts,
such as :

\begin{itemize}
    \item A scheduler (that may be able to preempt a task)
    \item Some communication protocols :
          \begin{itemize}
              \item Queues
              \item Messages
              \item events
          \end{itemize}
    \item Tasks (which include a priority flag !)
\end{itemize}

\subsubsection{Scheduler}
This is the main aspect of the RTOS, because this the task responsible to
schedule other tasks, while ensuring real times constraints. There's a lot of
different architecture here, each adding it's own set of positives or negatives
aspects.

\subsubsection{Communication protocols}
For this second concepts, we need to present the differents ways to send data
from one task to the other.

Since we're running multiple task in parallel, we can't define which
instruction will be executed before another on another task. Thus, standard
memory transfers, based on variables and pointers become unreliable. In fact,
most of the RTOS block these kind of transfers !\footnote{ The name may be
    different from one RTOS to the other, but the concepts remains the same. Here,
    we used the Zephyr RTOS naming convension, as we used this RTOS by after. }

Thus, we're forced to use thread-safe memory transfers, which are based on
buffers, FIFOs and other principle. Since the RTOS manage these, it can enable,
or disable some operations on the shared buffer. This is done to ensure memory
safety during the execution of the program.

There's indeed multiple type of transfers, depending the needs. The first,
Queues are FIFOs, and able to transfers large amount of data while ensuring the
order. The drawback of them is they're memory footprint which can be quite
large.

The second ones are similar, but only enable a small amount of data to be
transfered. And, as opposed to the FIFOs, when we overwrite the data, it's
deleted rather than pushed on the Queue. It's memory footprint is similar as
the size of a single object, but, it won't enable the conservations of previous
sample. Thus, we may skip data.

The last one are Events, which are simply bit. We flip them, to notify a thread
that something can, or can't be done.

\subsubsection{Tasks}
The last concept is the Task. This correspond to a thread that is going to be
executed on the CPU. For example, a task may be the main as we know.

Since tasks are handled by the RTOS, it's possible to run multiple tasks in
parallel, making control logic simpler. Thus, the timing logic (Timestamps...)
can be removed, and replaced by a delay. The RTOS will then pause the task and
execute another for the required duration.