\section{Digital part}
For this second part, the digital one we're going to look at the microcontroller mostly,
but also some parts of the whole digital subsystems. For this part, we mostly got inspired
by development kits, such as \cite{nRF5340DK}. Theses provide a great example on how to 
implement some IC on custom PCBs. 

Arround the MCU, we added some peripherals IC to fulfill our needs, for examples :
\begin{itemize}[noitemsep]
    \item An 16 Mb EEPROM, to store flight measurements.
    \item An RGB LED, to indicate status to the user.
\end{itemize}

To ensure the systems are working we sometimes need to modify some elements from the examples.
Theses changes are always documented in the datsheets of the components.

Here some examples of things we changed :
\begin{itemize}[noitemsep]
    \item   Change configuration bootstrap to select one mode of the other.
    \item   Configure power supplies needed.
    \item   Configure I2C addresses.
\end{itemize}

\subsection{Pin attribution}
For the last digital element, we're going understand how the pins were choosed on the MCU, and why.

First, we need to read the datasheets, and it's clearly explained that any peripheral can be routed to 
any pins.
Nonetheless, there's some pins that can designed for a specific function. For example, there is two pins
designed for high drain current, where the opposite direction (pull up) is standard. Theses pins are 
designed to handle high speed I2C ! So if we want to use fast I2C, it's clearly recommended to use them.

The remaining pins were placed arbitrary, because we'll changed that later ! \ref{sec:pin_swap}.

\subsection{Discrete logic}\label{subsec:dis_logic}
On the board, most of the logic is done in software by the MCU. But there's two hardware functions, related
to security features.

Theses are lathing the state of the pin with a DLATCH on the boot of the board, and an AND gate between the 
command of the engines and input of the drivers.

This enable us to block the start of engines in hardware rather than by software only. Thus, if the board 
is configured as debug mode, it won't be able to start engines, regardless of the software loaded.
